Practical Machine Learning Project
========================================================

Jingxi Chen



First, read in the data and do some exploratory analysis.
```{r,results='hide'}
data = read.csv('C:/Users/Ci/Desktop/R/coursera/practical machine learning/pml-training.csv',na.strings=c('NA',""))
test = read.csv('C:/Users/Ci/Desktop/R/coursera/practical machine learning/pml-testing.csv',na.strings=c('NA',""))
names(data)
head(data)
sapply(data,class)
```
I notice that there are hundreds of attributes but some of them are useless for prediction.
Of course, I need to set up the caret package and create data partition.
```{r}
require(caret)
inTrain = createDataPartition(y = data$classe, p = 0.6, list = F)
training = data[inTrain,]
testing = data[-inTrain,]
```
I only want to use part of the attributes. 

The numerical values of body moves are of interest for prediction.

```{r}
training = training[,which(sapply(data,  function( x) sum(is.na(x) )/length(x) )==0)]
training = training[,-(1:5)]
```
I am not so sure whether I should keep the 'num_window' variable. Let me do some visualization to explore it.

```{r}
require(ggplot2)
ggplot(data = training, aes(y = num_window, x = classe,color = classe))+geom_boxplot()

```
It seems to vary over different classe so I may keep it for now.
```{r}
ctr = trainControl(method='repeatedcv',repeats=3,number=5,classProbs = TRUE,savePre = T)
fit = train(trControl = ctr,data = training, classe~.,method='rf')
fit
confusionMatrix( predict(fit,testing),testing$classe)
answers = as.character(predict(fit,test))
```
I use repeated cross validation with the codes above and
I tried out different method to train the model and I figure out random forest does the best job. I expect it can predict with 99% or higher accuracy on new data set base on its performance on validation set.
